Canada’s Battle Against Car Theft: Progress Amid Persistent Challenges 

### 2024-12-02 paper/paper.qmd
DataAndMethodUpdate
update data and methods at second time

variable_description <- data.frame(
  Column = c(
    "_id", "EVENT_UNIQUE_ID", "REPORT_DATE", "OCC_DATE", "REPORT_YEAR",
    "REPORT_MONTH", "REPORT_DAY", "REPORT_DOY", "REPORT_DOW", "REPORT_HOUR",
    "OCC_YEAR", "OCC_MONTH", "OCC_DAY", "OCC_DOY", "OCC_DOW", "OCC_HOUR",
    "DIVISION", "LOCATION_TYPE", "PREMISES_TYPE", "UCR_CODE", "UCR_EXT",
    "OFFENCE", "MCI_CATEGORY", "HOOD_158", "LONG_WGS84", "LAT_WGS84"
  ),
  Description = c(
    "Unique row identifier for Open Data database",
    "Offence Number",
    "Date Offence was Reported",
    "Date of Offence",
    "Year Offence was Reported",
    "Month Offence was Reported",
    "Day of the Month Offence was Reported",
    "Day of the Year Offence was Reported",
    "Day of the Week Offence was Reported",
    "Hour Offence was Reported",
    "Year Offence Occurred",
    "Month Offence Occurred",
    "Day of the Month Offence Occurred",
    "Day of the Year Offence Occurred",
    "Day of the Week Offence Occurred",
    "Hour Offence Occurred",
    "Police Division where Offence Occurred",
    "Location Type of Offence",
    "Premises Type of Offence",
    "UCR Code for Offence",
    "UCR Extension for Offence",
    "Title of Offence",
    "MCI Category of Occurrence",
    "Identifier of Neighbourhood using City of Toronto's new 158 neighbourhood structure",
    "Longitude coordinate",
    "Latitude coordinate"
  )
)
# Render the table
kable(variable_description, col.names = c("Column", "Description")) %>% kable_styling(full_width = FALSE) %>%  column_spec(1, width = "4cm") %>% column_spec(2, width = "8cm")
```

>>>>

variable_description <- data.frame(
  Column = c(
    "X_id", "EVENT_UNIQUE_ID", "REPORT_DATE", "OCC_DATE", "REPORT_YEAR",
    "REPORT_MONTH", "REPORT_DAY", "REPORT_DOY", "REPORT_DOW", "REPORT_HOUR",
    "OCC_YEAR", "OCC_MONTH", "OCC_DAY", "OCC_DOY", "OCC_DOW", "OCC_HOUR",
    "DIVISION", "LOCATION_TYPE", "PREMISES_TYPE", "UCR_CODE", "UCR_EXT",
    "OFFENCE", "MCI_CATEGORY", "HOOD_158", "LONG_WGS84", "LAT_WGS84"
  ),
  Description = c(
    "Unique row identifier for Open Data database",
    "Offence Number",
    "Date Offence was Reported",
    "Date of Offence",
    "Year Offence was Reported",
    "Month Offence was Reported",
    "Day of the Month Offence was Reported",
    "Day of the Year Offence was Reported",
    "Day of the Week Offence was Reported",
    "Hour Offence was Reported",
    "Year Offence Occurred",
    "Month Offence Occurred",
    "Day of the Month Offence Occurred",
    "Day of the Year Offence Occurred",
    "Day of the Week Offence Occurred",
    "Hour Offence Occurred",
    "Police Division where Offence Occurred",
    "Location Type of Offence",
    "Premises Type of Offence",
    "UCR Code for Offence",
    "UCR Extension for Offence",
    "Title of Offence",
    "MCI Category of Occurrence",
    "Identifier of Neighbourhood using City of Toronto's new 158 neighbourhood structure",
    "Longitude coordinate",
    "Latitude coordinate"
  )
)
# Render the table
kable(variable_description, col.names = c("Column", "Description")) %>% kable_styling(full_width = FALSE) %>%  column_spec(1, width = "4cm") %>% column_spec(2, width = "8cm")
```
